Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-11-03 paper/main.tex
revision of result section

\todo[inline]{Limit for main text (intro and discussion) = ca. 3k words;
intro is about 1k words (with to dos)}

\todo[inline]{studies regarding naturalistic stimuli are dropped (Hasson,
2004: reverse correlation in PPA; Bartels, 2004: FFA and EBA). That should be
okay since we focus on the auditory part which should be clearer now; Hasson /
Bartels might shortly be mentioned in the discussion though}

@@

% Aziz (2008): place related sentences
To our knowledge only one study \citep{aziz2008modulation} investigated how
hemodynamic activity in the PPA differs between different semantic stimulus
categories occuring in spoken language.
% Aziz' stimuli
\cite{aziz2008modulation} used sentences that described generic or famous places
(e.g. ``The Taj Mahal faces a long thin reflecting pool''), faces (``Marilyn
Monroe has a large square jaw''), or objects (``The television has a long
antenna'').
% Aziz' tasks
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact.
% Aziz' results
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.
% wtf did Aziz really do?
\todo[inline]{lass uns bitte kurz im Gespräch über Aziz Paper gucken; die
relvanten Abschnitte sind in der PDF markiert. Ihre Method Section ist
``strange'' und im Grunde kommt überall nur uneinheitliche Grütze heraus; ich
blicke nicht durch, weshalb geschriebenes nicht vollständig korrekt sein wird;
so wie ich es verstanden habe, hat sie vier 2x2 ANOVAs den Unterschied zwischen
PPA und FFA angeguckt, aber diesen Unterschied im Kontrast zu object-related
Sentences (dortige Fig 3)}

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% three things in common
Nevertheless, the reviewed studies usually had three things in common.
% designed stimulus set
First, they employed a small sets of carefully chosen stimuli. Further, stimuli
were conceptualized to control confounding variables (e.g. color, luminance,
size, sentence length), a process that is often not reported in
detail.\todo{check that}
% block-design & task
Second, studies used block-designed paradigms to maximize detection power.
Further, they usually employed explicit perceptual judgment to keep participants
paying attention to the stimuli.
% averaging
Third, the reviewed studies averaged results across 7-11 subjects to improve
signal-to-noise ratio (SNR).
% disadvantages
Conceptualized stimuli, block-design experiments and the averaging approach have
their merits but also disandvantages.
% designed stimulus set
First, small sets of conceptualized stimuli presented on experimental blocks
poorly resembles our rich and multidimensional environment that our brains are
accommodated to [sonkusare2019naturalistic].
% block-design & task
Second, study participants can and will become aware about which perceptual
process is examined in the study by merely being exposed to the experimental
paradigm.
% inference: validity is poor
Thus, small sets of conceptualized stimuli and block-design experiment lack
external validity \citep{westfall2016fixing} as well as ecological validity
\citep{hasson2004intersubject}.
% disadvantage of averaging
Lastly, averaging data across subjects increases the SNR but does not
characterize brain functions at an individual level, a prerequisite for the
application of brain imaging methods in individual diagnostics (cf.
\cite{dubois2016building, eickhoff2020towards}).

% We are different
In this study, we operationalize the perception of landscapes and landmarks
(compared to e.g. faces and objects) differently from the reviewed studies by
using two fixed naturalistic stimuli (see \citep{hamilton2018revolution,
hasson2008neurocinematics, sonkusare2019naturalistic} for reviews).
% open research question
Here, we investigate if increased activation in the PPA correlates with
incidental ``spatial events'' in a Hollywood movie and its corresponding
audio-description (i.e. the audio-only variant of the movie).
% annotation
We annotated words spoken by the narrator of the audio-description of the movie
``Forrest Gump'' \citep{ForrestGumpMovie} as well as cuts and depicted locations
in the audio-visual movie to be able to operationalize the perception of
landscapes and landmarks (compared to e.g. persons and objects).
% public data
We then analyze publicly available data
(\href{http://www.studyforrest.org}{studyforrest.org}) from the same subjects
that listened to the audio-description and watched the movie during fMRI
scanning.
% first: group level AO
First, general linear model (GLM) contrasts based on the audio-description's
annotation are used to test if we could isolate the PPA with an auditory
stimulus on a group level.
% second: group level AV
Second as conceptual/cross-modal control, we compare results of the
audio-description to results based on the annotation of the movie.
% individual results
Lastly focussing on the audio-description, we compare results on the level of
individual subjects to results of a block-designed visual localizer experiment
done with the same individuals \citep{sengupta2016extension}.
% results
\todo[inline]{following paragraph will be similar to abstract and conclusion}
Our results demonstrate that (a), (b), (c).

@@

\subsection{Naturalistic stimuli annotation}
% todo stimuli were not designed for research purposes
Both natural stimuli were not design to isolate a specific brain area but to
entertain their audiences free from any perceptual or behavioral task.
% fixed stimuli and operationalization
We annotated the temporal structure of the fixed stimuls material to
operationalize the perception of different stimulus features (e.g. the
perception of landmarks and faces) and create GLM contrasts in the subsequent
data analysis.
% AO annotation
For the analysis of the AO data, we extended an publicly available annotation of
speech \citep{haeusler2020speechanno} by further annotating words spoken by the
audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content.
% categories in detail
Nouns were categorized by the verbal clue they provide about the cinematographic
scene's environment (\texttt{geo}, \texttt{geo-room}; \texttt{setting\_new},
\texttt{setting\_old}), its inherent persons (e.g. \texttt{female},
\texttt{male}, \texttt{persons}), a person's body or worn clothes
(\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a scene's
inherent objects (\texttt{object}, \texttt{furniture}).
% why and how of categories 1
Some categories were created to reflect the six stimulus categories used in the
visual localizer experiment (e.g. \texttt{geo}, \texttt{object}).
% why and how of categories 2
Other categories were created to semantically cluster some remaining nouns into
additional categories (e.g. \texttt{fname}, \texttt{furniture})
% problem with hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
not just words that describe an abstract location (e.g. ``in Greenbow'') or a
setting as whole (e.g. ``the platoon wades through a rice field'', ``in a
disco''). They also comprise words that could count as a member of another
categories in case the narrator uses these words to indicate a switch from one
setting to another (e.g. ``near an old bus'').
% reference to table with rules and examples
A complete overview of all 19 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with counts
The resulting counts for the whole stimulus and the eight stimulus segments used
during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.

@@

\subsubsection{first-level}

\paragraph{Regressors}

@@

% AO: events
For the analysis of the AO stimulus, we created regressors correlating with the
occurrence of descriptive nouns spoken by the narrator that were added to the
original annotation of speech \citep{haeusler2020speechanno}.
% AV events
For the AV stimulus, we created regressors correlating with movie cuts provided
by another previously published annotation \citep{haeusler2016cutanno}.
% https://github.com/psychoinformatics-de/studyforrest-data-annotations/blob/master/code/researchcut2segments.py}

@@

% AV events
To create regressors for the AV analysis, we categorized the depicted location
in the frame following one of the 869 cuts into five categories (see Table
\ref{tab:av-events}): 1) a cut into an unfamiliar setting (\texttt{vse\_new}),
2) a cut into a familiar setting (\texttt{vse\_old}), 3) a switch of room/locale
within a setting (\texttt{vlo\_ch}), 4) a cut to an unfamiliar perspective
(\texttt{vpe\_new}), and 5) a cut to a familiar perspective (\texttt{vpe\_old}).
% null regressor
Here again, a null regressor was chosen for segment if it did not contain an
event of specific category.
% no cut condition: intro
A sixth regressors (\texttt{no\_cut}) serving a control condition and to create
negative control contrasts. Frames within movie shots lasting at least
\unit[20]{s} were pseudo-randomly chosen by the following rationale:
% how they were fitted
a \texttt{no\_cut} event had to have a minimum distance of \unit[10]{s} to a
movie cut and to another \texttt{no\_cut} event.
% reference to table
A short explanation and counts of these six categories modeled as impulse
events, and six additional event categories for low-level auditory and visual
features of the movie (here again continuous bins lasting \unit[40]{ms}) can be
found in Table \ref{tab:av-events}.
% modeling of regressors from events
Events of both stimuli were convolved with a double gamma hemodynamic response
function (HRF).

@@

\paragraph{AO: COPEs}

 \todo[inline]{I wonder whether we should make a general
    point: The construction of contrasts of interests feels "messy". But this is
    a consequence of the inability to filter the stimulus material. That "messy"
    part is usually not obvious from a manuscript.  Here we have a fixed,
complex stimulus, and we have to operationalize our questions with whatever we
have at hand. This is not necessarily exact, and looking at the robustness is a
feature, not a problem}

\todo[inline]{send me to hell for the following paragraphs but it is detailed at
least}

% we did a couple of contrasts and why
We created eight $t$-contrasts for the AO stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}) to test the stability of results across different
contrasts and exclude accidental \todo{MIH: what does this mean? exclude incidental findings? sounds like we made it look pretty...} findings.
% contrasts are of different quality
We assumed all contrasts could in principle isolate the PPA. Nevertheless, we
also assumed contrasts would differ in their isolation performance because they
differ in how well the included event categories reflect on average the
preferred stimulus type processed in the PPA.
% selection of the primary contrast
Thus for each stimulus, we chose one ``primary contrast'' for a detailed report
and discussion of the group-level and subject-specific results. Primary
contrasts were chosen based on how well the used categories on average were
assumed to match the preferred stimulus type in balance with the amount of
available data / events.

\todo[inline]{compare the following with annotation \& Discussion}
% intro
In context of the AO stimulus, the categories \texttt{se\_new} and
\texttt{se\_old} were problematic for a couple of reasons and thus are not
included in the primary contrast:
% sparse auditory, rich visually
(a) they often only vaguely describe a scene (e.g. ``black and white film
recordings'', ``in Greenbow'') whereas a picture of the verbally described scene
would be perceptually richer,
% hierarchical categories
(b) They also comprise words that could count as a member of another categories
in case the narrator uses these words to indicate a switch from one setting to
another (e.g. ``Jenny as teenager'', ``near an old bus'')
% soundscapes forestalls narrator
(c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that already cue a change of settings.
cuts but in AO stimulus
% conclusion
Hence, we assumed contrasts that (exclusively) used these two categories would
induce noise and would be less successful in isolating the PPA.

% negative control contrasts
Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created as negative
controls to test if increased activation in the PPA was correlated with
moments of cuts and therefore possibly correlated with a accompanying change in
the soundscape.\todo{all essentially almost null results}

% furniture
We did not use the category ``furniture'' (\texttt{furn}) as a
regressor of interest in any contrasts because nouns in this category were
usually big and heavy. In a serial stream of auditory information, participants
could perceive furniture-related nouns as either a geometry-defining local scene
element or as an isolated object. Hence we did not use this category as
regressor of interest to reduce noise.

\begin{table*}[t]
\caption{Contrasts of parameter estimates for the analysis of the audio-only stimulus (AO).
Contrast 1-8 aim to isolate the PPA (\texttt{all non-geo} = body, bodypart,
    fahead, object, sex\_f, sex\_m).
Contrasts 9-13 serve as negative control at the moments of movie cuts that could
    correlate with changes of the audio tracks soundscape (see Table \ref{tab:av-contrasts}).}

\label{tab:ao-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & geo, groom > all non-geo & PPA \tabularnewline
2 & geo, groom, se\_new > all non-geo & PPA \tabularnewline
3 & groom, se\_new, se\_old > all non-geo & PPA \tabularnewline
4 & geo > all non-geo & PPA \tabularnewline
5 & groom > all non-geo & PPA \tabularnewline
6 & se\_new > all non-geo & PPA \tabularnewline
7 & se\_new, se\_old > all non-geo & PPA \tabularnewline
8 & se\_new > se\_old & PPA \tabularnewline
9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
10 & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
11 & vse\_new > vse\_old & control at moments of cuts \tabularnewline
12 & vse\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
13 & vse\_new, vpe\_new > vpe\_old & control at moments of cuts \tabularnewline
\end{tabular}
\end{table*}

\paragraph{AV: COPEs}

\todo[inline]{I think it's better to explain the rationale of the regressors
here in the context of the contrasts and not already above in the list of
created regressors}

% intro
In context of the AV stimulus, we categorized the frames following a movie cut
irrespective of their concrete visual content and thus without controlling
confounding variables (e.g. presence of faces). The rationale that this
procedure would still be able to isolate the PPA was twofold.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movies tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Moreover, shots within a recurring locale or setting tend to shift to depicting
persons and objects (\texttt{vpe\_old}) more relevant to the evolved plot
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was simply that activity in the PPA is greater
when participants view novel versus repeated scenes or view-points.
\citep{epstein1999parahippocampal}.
% hence, the following contrasts
Hence, we created varying contrasts comparing a setting occurring for the first
time and cuts within a locale depicted for the first time to cuts into recurring
settings and cuts within a recurring locale.
% negative control
Five additional $t$-contrasts we created for negative control purposes (see
Table \ref{tab:av-contrasts}).
\todo[inline]{all null results; except cope 10 (nouns of narrator but in movie):
right PPA, bilat sup. lat. occ. cortec, LOC (l/r), right superior parietal
lobe).}

@@

\paragraph{alignment etc.}

% single subjects (for Bland-Altman-Plots) 1st level
The GLM analysis that fitted each voxel's time course separately for each
subject and segment was performed in functional space preserving the orientation
of the EPI images.
% two ways of co-registration
We co-registered the subjects in two ways.
% subject template (for Bland-Altman-Plot of unthresholded maps)
% \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
On the one hand, subject-specific BOLD T2* time series were anatomically aligned
via linear transformation to a subject-specific, study-specific T2* template (cf
. \citep{sengupta2016extension}).
% group template (for group and individual brain slices)
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
On the other hand, time series were aligned via non-linear transformation to a
study-specific T2* group template (cf. \citep{hanke2014audiomovie}).
% MNI152
This group template was co-registered to the MNI 152 template with an affine
transformation (12 degrees of freedom) to facilitate visualization and
identification of cortical structures.

@@

% study goal
The goal of this study was to investigate if increased hemodynamic activity in
the PPA correlates with spatial information presented under more ecological
valid conditions.\todo{cautious phrasing but still problematic: looking for
confirmation}
% what we did
We used annotations of a \unit[2]{h} movie and it's temporally aligned
audio-description to create canonical GLM contrasts of modeled hemodynamic
activity resembling analyses of previous studies using simplified stimuli.
% comparison AO & AV
We compare these results on a group and individual level to results gained from
an audio-visual naturalistic stimulus and to results from a dedicated visual
localizer experiment.

\todo[inline]{the big question: where to put the ``stability of contrasts''? any
position in the results has pro's and con's; at the moment they come last}

\subsection{primary contrasts}

\todo[inline]{paragraphs start with 1-2 sentences that set up the question
that the paragraph answers; e.g. ``To verify that there are no artifacts''}

\todo[inline]{middle of paragraph presents data and logic that pertain the
question}

@@

\subsection{stability contrasts}

>>>>

\todo[inline]{Limit for main text (intro and discussion) = ca. 3k words;}

\todo[inline]{studies regarding naturalistic stimuli are dropped (Hasson, 2004:
reverse correlation in PPA; Bartels, 2004: GLM, FFA and EBA). That should be okay since we focus on the auditory part which should be clearer now; Hasson /
Bartels might shortly be mentioned in the discussion though}

@@

% Aziz (2008): place related sentences
To our knowledge only one study \citep{aziz2008modulation} investigated how
hemodynamic activity in the PPA differs between different semantic stimulus
categories occurring in spoken language.
% Aziz' stimuli
\cite{aziz2008modulation} used sentences that described generic or famous places
(e.g. ``The Taj Mahal faces a long thin reflecting pool''), faces (``Marilyn
Monroe has a large square jaw''), or objects (``The television has a long
antenna'').
% Aziz' tasks
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact.
% Aziz' results
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.
% wtf did Aziz really do?
\todo[inline]{lass uns bitte kurz im Gespräch über Aziz Paper gucken; die
relvanten Abschnitte sind in der PDF markiert. Ihre Method Section ist
``strange'' und im Grunde kommt überall nur uneinheitliche Grütze heraus; ich
blicke nicht durch, weshalb geschriebenes nicht vollständig korrekt sein wird;
so wie ich es verstanden habe, hat sie vier 2x2 ANOVAs den Unterschied zwischen
PPA und FFA angeguckt, aber diesen Unterschied im Kontrast zu object-related
Sentences (dortige Fig 3)}

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% three things in common
Nevertheless, the reviewed studies usually had three things in common.
% designed stimulus set
First, they employed a small sets of carefully chosen stimuli. Further, stimuli
were conceptualized to control confounding variables (e.g. color, luminance,
size, sentence length), a process that is often not reported in
detail.\todo{really? check that}
% block-design & task
Second, studies used block-designed paradigms to maximize detection power.
Further, they usually employed explicit perceptual judgment to keep participants
paying attention to the stimuli.
% averaging
Third, the reviewed studies averaged results across 7-11 subjects to improve
signal-to-noise ratio (SNR).
% disadvantages
Conceptualized stimuli, block-design experiments and the averaging approach have
their merits but also disadvantages.
% designed stimulus set
First, small sets of conceptualized stimuli presented on experimental blocks
poorly resembles our rich and multidimensional environment that our brains are
accommodated to [sonkusare2019naturalistic].
% block-design & task
Second, study participants can and will become aware about which perceptual
process is examined in the study by merely being exposed to the experimental
paradigm.
% inference: validity is poor
Thus, small sets of conceptualized stimuli and block-design experiment lack
external validity \citep{westfall2016fixing} as well as ecological validity
\citep{hasson2004intersubject}.
% disadvantage of averaging
Lastly, averaging data across subjects increases the SNR but does not
characterize brain functions at an individual level, a prerequisite for the
application of brain imaging methods in individual diagnostics (cf.
\cite{dubois2016building, eickhoff2020towards}).

% Open research question
In this study, we investigate if increased activation in the PPA correlates with
incidental ``spatial information'' in the audio-description of the Hollywood
movie ``Forrest Gump'' (i.e. the audio-only variant of the movie) and, for
cross-modal comparison, in the (actual) audio-visual movie (itself).
% we are different
Since we did not design the given naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews) for optimal localization performance of
the PPA, we operationalize the perception of landscapes and landmarks (compared
to e.g. faces and objects) differently from the reviewed studies.
% operationalization via annotation
Here, we annotated words spoken by the narrator of the audio-description as well
as cuts and depicted locations in the movie.
% public data
We then analyze publicly available data
(\href{http://www.studyforrest.org}{studyforrest.org}) from the same subjects
that listened to the audio-description and watched the movie during fMRI
scanning.
% first: group level AO
First, general linear model (GLM) contrasts based on the audio-description's
annotation are used to test if we could isolate the PPA with an auditory
stimulus on a group level.
% second: group level AV
Second as conceptual/cross-modal control, we compare results of the
audio-description to results based on the annotation of the movie.
% individual results
Lastly focussing on the audio-description, we compare results on the level of
individual subjects to results of a block-designed visual localizer experiment
done with the same individuals \citep{sengupta2016extension}.
% results
\todo[inline]{following paragraph will be similar to abstract and conclusion}
Our results demonstrate that (a), (b), (c).

@@

\subsection{Naturalistic stimuli annotation}
% todo stimuli were not designed for research purposes
Both natural stimuli were not design to isolate a specific brain area but to
entertain their audiences free from any perceptual or behavioral task.
% fixed stimuli and operationalization
We annotated the temporal structure of the fixed stimuls material to
operationalize the perception of different stimulus features (e.g. the
perception of landmarks and faces) and create GLM contrasts in the subsequent
data analysis.
% AO annotation
For the analysis of the AO data, we extended an publicly available annotation of
speech \citep{haeusler2020speechanno} by further annotating words spoken by the
audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content.
% categories in detail
Nouns were categorized by the verbal clue they provide about the cinematographic
scene's environment (\texttt{geo}, \texttt{geo-room}; \texttt{setting\_new},
\texttt{setting\_old}), its inherent persons (e.g. \texttt{female},
\texttt{male}, \texttt{persons}), a person's body or worn clothes
(\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a scene's
inherent objects (\texttt{object}, \texttt{furniture}).
% why and how of categories 1
Some categories were created to reflect the six stimulus categories used in the
visual localizer experiment (e.g. \texttt{geo}, \texttt{object}).
% why and how of categories 2
Other categories were created to semantically cluster some remaining nouns into
additional categories (e.g. \texttt{fname}, \texttt{furniture})
% problem with hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
not just words that describe an abstract location (e.g. ) or a setting as whole
(e.g. ``in Greenbow'', ``in a disco'', ``the platoon wades through a rice
field''). They also comprise words that could count as a member of another
categories in case the narrator uses these words to indicate a switch from one
setting to another (e.g. ``near an old bus'').
% reference to table with rules and examples
A complete overview of all 19 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with counts
The resulting counts for the whole stimulus and the eight stimulus segments used
during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.

@@

@@

% first level analysis
% regressors
% AO: events
For the analysis of the AO stimulus, we created regressors correlating with the
occurrence of descriptive nouns spoken by the narrator that were added to the
original annotation of speech \citep{haeusler2020speechanno}.
% AV events
For the AV stimulus, we created regressors correlating with movie cuts provided
by another previously published annotation \citep{haeusler2016cutanno}.
% https://github.com/psychoinformatics-de/studyforrest-data-annotations/blob/master/code/researchcut2segments.py}

@@

% AV regressors/events
To create regressors for the AV analysis, we categorized the depicted location
in the frame following one of the 869 cuts into five categories (see Table
\ref{tab:av-events}): 1) a cut into an unfamiliar setting (\texttt{vse\_new}),
2) a cut into a familiar setting (\texttt{vse\_old}), 3) a switch of room/locale
within a setting (\texttt{vlo\_ch}), 4) a cut to an unfamiliar perspective
(\texttt{vpe\_new}), and 5) a cut to a familiar perspective (\texttt{vpe\_old}).
% null regressor
Here again, a null regressor was chosen for segment if it did not contain an
event of specific category.
% no cut condition: intro
A sixth regressors (\texttt{no\_cut}) serving a control condition and to create
negative control contrasts. Frames within movie shots lasting at least
\unit[20]{s} were pseudo-randomly chosen by the following rationale:
% how they were fitted
a \texttt{no\_cut} event had to have a minimum distance of \unit[10]{s} to a
movie cut and to another \texttt{no\_cut} event.
% reference to table
A short explanation and counts of these six categories modeled as impulse
events, and six additional event categories for low-level auditory and visual
features of the movie (here again continuous bins lasting \unit[40]{ms}) can be
found in Table \ref{tab:av-events}.
% modeling of regressors from events
Events of both stimuli were convolved with a double gamma hemodynamic response
function (HRF).

@@

\todo[inline]{MH: construction of contrasts of interests feels "messy";
     consequence of the inability to filter the stimulus material. That "messy"
     part is usually not obvious from a manuscript. Here we have a fixed,
     complex stimulus, and we have to operationalize our questions with whatever
     we have at hand. This is not necessarily exact, and looking at the
 robustness is a feature, not a problem; COH: did not change a lot of text tbh
 but should be clearer now.}

% we have fixed stimuli
Compared to previous studies we did not design the stimulus material and
experimentally controlled conditions for the
purpose of optimal localization performance since we used fixed stimuli.
% 8 + 5 contrasts
We created eight $t$-contrasts for the AO stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}) to operationalize ``spatial perception'' compared to
``non-spatial'' perception.\todo{big ouff\dots}
% test for robustness
Creating more than just one contrast for the two
fixed stimuli also let us test for/the robustness of our results across varying
ways operationalization.
% contrasts are of different quality
We assumed all contrasts could in principle isolate the PPA. Nevertheless, we
also assumed contrasts would differ in their isolation performance because they
differ in how well the included event categories reflect on average the
preferred stimulus type processed in the PPA.
% selection of the primary contrast
Thus for each stimulus, we chose one ``primary contrast'' for a detailed report
and discussion of the group-level and subject-specific results. Primary
contrasts were chosen based on how well the used categories on average were
assumed to match the preferred stimulus type in balance with the amount of
available data / events.

% AO COPEs: intro
In context of the AO stimulus, the categories \texttt{se\_new} and
\texttt{se\_old} were problematic for three reasons and thus are not included in
the primary contrast:
% sparse auditory, rich visually
(a) they often only vaguely describe a scene (e.g. ``in Greenbow'', ``in a
disco'', ''black and white film recordings'') whereas a picture of the verbally
described scene would be perceptually richer,
% hierarchical categories
(b) they also comprise words that could count as a member of another category in
case the narrator uses these words to indicate a switch from one setting to
another (e.g. ``Jenny as teenager'', ``near an old bus'')
% soundscapes forestalls narrator
(c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that already cue a change of settings.  cuts but in AO stimulus
% conclusion
Hence, we assumed contrasts that (exclusively) used these two categories would
induce noise and would be less successful in isolating the PPA.
% furniture
We did not use the category ``furniture'' (\texttt{furn}) as a
regressor of interest in any contrasts because nouns in this category were
usually big and heavy. In a serial stream of auditory information, participants
could perceive furniture-related nouns as either a geometry-defining local scene
element or as an isolated object. Hence we did not use this category as
regressor of interest to reduce noise.
% negative control contrasts
Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created as negative
controls to test if increased activation in the PPA was correlated with
moments of cuts and therefore possibly correlated with a accompanying change in
the soundscape.

\begin{table*}[t]
\caption{Contrasts of parameter estimates for the analysis of the audio-only
    stimulus (AO). Contrast 1-8 aim to isolate the PPA (\texttt{all non-geo} =
    body, bodypart, fahead, object, sex\_f, sex\_m).
    Contrasts 9-13 serve as negative control at the moments of movie cuts that
    could correlate with changes of the audio tracks soundscape (see Table
    \ref{tab:av-contrasts}).}
\label{tab:ao-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & geo, groom > all non-geo & PPA \tabularnewline
2 & geo, groom, se\_new > all non-geo & PPA \tabularnewline
3 & groom, se\_new, se\_old > all non-geo & PPA \tabularnewline
4 & geo > all non-geo & PPA \tabularnewline
5 & groom > all non-geo & PPA \tabularnewline
6 & se\_new > all non-geo & PPA \tabularnewline
7 & se\_new, se\_old > all non-geo & PPA \tabularnewline
8 & se\_new > se\_old & PPA \tabularnewline
9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
10 & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
11 & vse\_new > vse\_old & control at moments of cuts \tabularnewline
12 & vse\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
13 & vse\_new, vpe\_new > vpe\_old & control at moments of cuts \tabularnewline
\end{tabular}
\end{table*}

\todo[inline]{MH: I think it's better to explain the rationale of the regressors
here in the context of the contrasts and not already above in the list of
created regressors: COH: yes, I checked that. Above is just a short
list/explanation except for ``no cut'' condition. imo it makes more sense to
explain it there but maybe I cannot get the reason why you think it fits here
better}

% AV COPEs: intro
In context of the AV stimulus, we categorized the frames following a movie cut
irrespective of their concrete visual content and thus without controlling
confounding variables (e.g. presence of faces). The rationale that this
procedure would still be able to isolate the PPA was twofold.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movies tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Moreover, shots within a recurring locale or setting tend to shift to depicting
persons and objects (\texttt{vpe\_old}) more relevant to the evolved plot
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was simply that activity in the PPA is greater
when participants view novel versus repeated scenes or view-points.
\citep{epstein1999parahippocampal}.
% hence, the following contrasts
Hence, we created varying contrasts comparing a setting occurring for the first
time and cuts within a locale depicted for the first time to cuts into recurring
settings and cuts within a recurring locale.
% negative control
Five additional $t$-contrasts we created for negative control purposes
(see Table \ref{tab:av-contrasts}) by using regressors based on regressors of
the AO stimulus.

@@

% alignments
% single subjects (for Bland-Altman-Plots) 1st level
The GLM analysis that fitted each voxel's time course separately for each
subject and segment was performed in functional space preserving the orientation
of the EPI images.
% two ways of co-registration
We co-registered the subjects in two ways.
% subject template (for Bland-Altman-Plot of unthresholded maps)
% \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
On the one hand, subject-specific BOLD T2* time series were anatomically aligned
via linear transformation to a subject-specific, study-specific T2* template
(cf. \citep{sengupta2016extension}).
% group template (for group and individual brain slices)
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
On the other hand, time series were aligned via non-linear transformation to a
study-specific T2* group template (cf. \citep{hanke2014audiomovie}).
% MNI152
This group template was co-registered to the MNI 152 template with an affine
transformation (12 degrees of freedom) to facilitate visualization and
identification of cortical structures.

@@

\todo[inline]{I consider tables of significant clusters for all contrasts as
overkill. Maybe in ``supporting material'' or reference to dataset?  all sign.
clusters of all contrasts are in the comments}

% study goal
The goal of this study was to investigate if increased hemodynamic activity in
the PPA correlates with spatial information presented under more ecological
valid conditions.\todo{cautious phrasing but still problematic: looking for
confirmation}
% what we did
We annotated a \unit[2]{h} movie and its temporally aligned audio-description to
create GLM contrasts similar to previous studies that used simplified stimuli.
% group level
On a group average level, we compare results gained from both naturalistic
stimuli to results gained from a visual localizer experiment.
% individual level
On the level single subjects, we also assess localization performance of a
``visual area'' using the auditory stimulus.

% all AO contrasts
% 1 PPA (l/r); RSC (l/r), LOC (l/r)
% 2 PPA (l/r); RSC (l/r), LOC (l/r), r. sup.temp.C., r.fr.pole; putamen; etc
% 3 PPA (l/r); RSC (l/r), LOC (l/r),l&r sup.temp.C., anterior cing., paracing.
% 4 PPA (l/r); RSC (l/r), LOC (l/r)
% 5 PPA (l/r); RSC (l/r), LOC (-/-)
% 6 PPA (l/r); RSC (l/r), LOC (l/-), l&r sup.temp.C.; medial pref. c., precun
% 7 PPA (-/-); RSC (l/r), LOC (l/-), l&r sup.temp.C
% 8 PPA (-/-); RSC (-/-), LOC (-/-)
% ---------- control contrasts ----------
% 9 PPA (-/-); RSC (-/r), LOC (-/-), left pars triangularis
%10 PPA (-/-); RSC (-/-), LOC (-/-)
%11 PPA (-/-); RSC (-/-), LOC (-/-),
%12 PPA (-/-); RSC (-/-), LOC (-/-), right posterior hippocampus
%13 PPA (-/-); RSC (-/-), LOC (-/-) results: PPA

% all AV contrasts
% 1 PPA (l/r); RSC (l/r), LOC (l/r), VisC (l/r),
% intracalcarine, cuneal, ling.c
% 2 PPA (l/r); RSC (-/-), LOC (l/r), VisC (-/-)
% 3 PPA (l/r); RSC (-/-), LOC (-/-), VisC (-/r), occ. fusisf. g.
% 4 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), lingual g., occ. fusif. g.
% 5 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), occ. fusif. g.
% ---------- control contrasts ----------
% 6 nothing
% 7 nothing
% 8 nothing
% 9 nothing
%10 se_new > se_old (nouns but in AV stimulus):
% LOC (l/r) right PPA, bilateral sup. lat. occ. c., sup. parietal lobe (right)

\subsection{Group results (all AO + AV PPA contrasts)}

\todo[inline]{paragraphs start with 1-2 sentences that set up the question
that the paragraph answers; e.g. ``To verify that\dots''}

\todo[inline]{middle of paragraph presents data \& logic that pertain the
question}

@@
